Under-ice acoustic navigation using real-time model-aided range estimation

### 2022-02-21 manuscript/main.tex
made figs bigger, easy to see details

\begin{figure}[h!]
	\centering
	\includegraphics[width=\reprintcolumnwidth]{figs/Fig2.pdf}
	\caption{A schematic overview of the Integrated Communication and Navigation Network (ICNN), which provides joint data-transfer and tracking between AUV and a human decision maker at Topside.}
	\label{fig:icnnOverview}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{figs/modem-chart.pdf}
  \caption{An overview of the modem experiment by source and receiver depth and position. The black column on the left, $tx$, shows the source depth, $z_s$, with the total number of transmissions. The column on the right, $rx$, shows the receivers with the number of successful decodings and the percent success rate, defined as the ratio of decoded to detected. The orientation of the triangles\textemdash sideways, upwards, and downwards\textemdash corresponds to depths of 20, 30, and 90 m.}
  \label{fig:overview}
  \end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\reprintcolumnwidth]{figs/range-error-insitu.pdf}
  \caption{The real-time range error by source (rows: 20, 30, and 90 m) and receiver (columns: 30 and 90 m) pairings for both sound speed estimates used during ICEX20. The amount of communication events is notated in the top right of each panel. The dashed line indicates no range error, and the boundary drawn indicates scope of the range error as a function of one way travel time.}
  \label{fig:range-error-insitu}
\end{figure}

@@

\subsubsection{Source depth of 20 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\reprintcolumnwidth]{figs/raytrace-3env-zs-20.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 20 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs20}
\end{figure}

@@

\subsubsection{Source depth of 30 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\reprintcolumnwidth]{figs/raytrace-3env-zs-30.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 30 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs30}
\end{figure}

@@

\subsubsection{Source depth of 90 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\reprintcolumnwidth]{figs/raytrace-3env-zs-90.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 90 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs90}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figs/range-error-allMethods.pdf}
\caption{The post-processed pseudorange error; the rows share receiver depth; the columns share source depth. The dashed gray line shows no error. The shaded region connects the range performance across all events.}
\label{fig:rangeError}
\end{figure}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\columnwidth]{figs/Fig2.pdf}
	\caption{A schematic overview of the Integrated Communication and Navigation Network (ICNN), which provides joint data-transfer and tracking between AUV and a human decision maker at Topside.}
	\label{fig:icnnOverview}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\columnwidth]{figs/modem-chart.pdf}
  \caption{An overview of the modem experiment by source and receiver depth and position. The black column on the left, $tx$, shows the source depth, $z_s$, with the total number of transmissions. The column on the right, $rx$, shows the receivers with the number of successful decodings and the percent success rate, defined as the ratio of decoded to detected. The orientation of the triangles\textemdash sideways, upwards, and downwards\textemdash corresponds to depths of 20, 30, and 90 m.}
  \label{fig:overview}
  \end{figure}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\columnwidth]{figs/range-error-insitu.pdf}
  \caption{The real-time range error by source (rows: 20, 30, and 90 m) and receiver (columns: 30 and 90 m) pairings for both sound speed estimates used during ICEX20. The amount of communication events is notated in the top right of each panel. The dashed line indicates no range error, and the boundary drawn indicates scope of the range error as a function of one way travel time.}
  \label{fig:range-error-insitu}
\end{figure}

@@

\subsubsection{Source depth of 20 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\columnwidth]{figs/raytrace-3env-zs-20.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 20 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs20}
\end{figure}

@@

\subsubsection{Source depth of 30 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\columnwidth]{figs/raytrace-3env-zs-30.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 30 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs30}
\end{figure}

@@

\subsubsection{Source depth of 90 m}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=\columnwidth]{figs/raytrace-3env-zs-90.pdf}
  \caption{Eigenrays for beacon-to-beacon events for each sound speed with a nominal source depth of 90 m over a total ray fan in gray. The beacons are highlighted in color/marker coding in Fig. \ref{fig:overview}.}
  \label{fig:raytrace-zs90}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\columnwidth]{figs/range-error-allMethods.pdf}
\caption{The post-processed pseudorange error; the rows share receiver depth; the columns share source depth. The dashed gray line shows no error. The shaded region connects the range performance across all events.}
\label{fig:rangeError}
\end{figure}
